---
title: "Compare two list"
author: "Chia-Ching Chou"
date: "March 30, 2015"
output:
  html_document:
    keep_md: yes
---
This is my note for R learning. 
Question: I want to compare two list of Enzymes use in two different sequence. I want to know what enzyme are share bewteen them. I want to know what is work in just one of them.

```{r, echo=FALSE}
setwd("~/Dropbox/Scripts/genomicClass/My Note")
```
Here are the example R code to compare two list.

```{r}

A = c("Dog", "Cat", "Mouse")
B = c("Tiger","Lion","Cat")
A %in% B
intersect(A,B) # in both A and B
setdiff(A,B) # A have but not in the B

```

Example from this place:
http://stackoverflow.com/questions/17598134/compare-two-lists-in-r
The csv files make from NEB cutter by fellowing steps.
1. past sequence into NEB cutter.
2. click custom digest.
3. Select table of the Enzymes.
4. Past Text into Excel with 4 col selected.
5 Save as csv file. (Note: the first col will be blank. The first row will shift one col. correct by hand.)
```{r}
y<- read.csv("YFCmycRList.csv", head=F)
b<- read.csv("BYP200RList.csv", head=F)
ry <- y[,1]
rb <- b[,1]
tfInry <- ry %in% rb # ry element match in rb will T else will F.
inBothyb <- intersect(ry,rb)
inryNotInB <- setdiff(ry,rb)

inrbNotIny <- setdiff(rb,ry)
suby<- y[!tfInry,] ## use logical list to subset y (Here I use "!" to sub set F row from y)
# This sub set will have same enzyme as setdiff(ry,rb)

```






